% arara: xelatex

\documentclass{resume}
\usepackage{ctex}
% \usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yinya Wang (王胤雅)}

\basicInfo{
	\email{201911010205@mail.bnu.edu.cn} \textperiodcentered\
	\phone{(+86) 15907464032} \textperiodcentered\
	% \linkedin[billryan8]{https://www.linkedin.com/in/billryan8}
}

\section{\faFemale\ Personal Summary}
I have achieved excellent academic performance during my studies, with a positive and optimistic attitude. I have a deep passion for mathematics and a broad knowledge of various mathematical fields. I focus on using computer technologies to improve efficiency in both life and study. I hope to continue exploring my academic interests and delve into more advanced mathematical theories and applications in the future.

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Beijing Normal University}, Beijing, China}{2019 -- Present}
Bachelor’s degree in Mathematics and Applied Mathematics, expected graduation in June 2025. Awarded academic scholarships 4 times.

\section{\faBook\ Academic Performance}
\begin{itemize}
	\item GPA: 3.6/4.0, Top 20\% (Ranked 29/140);
	\item Completed 20+ courses in pure mathematics, including Functional Analysis (95 points), Selected Topics in Markov Processes (93 points), Real Variable Function (93 points), etc.;
	\item Completed 2 courses in applied mathematics, including Parallel Computing (95 points) and Mathematical Modeling (91 points).
\end{itemize}

\section{\faThumbsOUp\ Skills}
\begin{itemize}
	\item Able to program with C, Python, and Lua;
	\item Skilled in \LaTeX\ for document preparation;
	\item Experienced in using Git for code management;
	\item TOEFL score: 92.
\end{itemize}

\section{\faLightbulbO\ Research Experience}
\datedsubsection{Independent Research}{2020.01-2021.03}
Research on Litter Decomposition Based on the Olson Model, published in the proceedings of the 5th International Conference on Economic Management and Green Development.

\datedsubsection{Undergraduate Research Project}{2022.06-2023.05}
Under the supervision of Professor Hui He, participated in research on the convergence rate estimation of random branching walk counting measures.

\datedsubsection{Beijing Innovation Project}{2023.06-2024.05}
Under the supervision of Professor Xinxin Chen, involved in research on large deviation problems of branching Brownian motion level sets.

\section{\faBell\ Campus Activities}
\datedsubsection{Club Activities}{2021.10-2022.08}
\begin{itemize}
	\item Member of the OM Society, actively participating in activities related to mathematics competitions;
	\item Member of the Psychological Department in the Faculty of Science, organizing and planning various mental health activities.
\end{itemize}

\datedsubsection{Excellence Training Camp}{2021.10-2022.08}
Successfully participated in and completed the Excellence Training Camp at Beijing Normal University, enhancing both academic and leadership skills.

\datedsubsection{Snowflake Messenger}{2022}
Completed on-campus volunteer training and became a Snowflake Messenger, actively helping fellow students.

\section{\faHeartO\ Awards}
\datedline{\nth{1} Freshman Scholarship, Second Prize}{2019年}
\datedline{\nth{2} JingShi Scholarship, Second Prize}{2022年}
\datedline{\nth{3} National Undergraduate Mathematics Contest, Third Prize}{2023年}
\datedline{\nth{4} Competition Scholarship, Second Prize}{2023年}

\section{\faInfo\ Other Information}
\begin{itemize}[parsep=0.5ex]
	\item \faGithub: \href{http://github.com/evawyy}{http://github.com/evawyy}
	\item Languages: English (Fluent), Chinese (Native).
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
